A Simple Minibatch Acceptance Test for MCMC

### 2016-05-19 nips_2016.tex
finish append C and D

\section{Logistic Regression Experiment Details}\label{app:logistic}

{\color{blue}
Daniel: TODO
}

@@

{\color{blue}
Daniel: TODO
}

% Daniel: here are example LaTeX codes for figures and tables if we want to use them.
%\begin{figure}[h]
%  \centering
%  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
%  \caption{Sample figure caption.}
%\end{figure}
%\begin{table}[t]
%  \caption{Sample table title}
%  \label{sample-table}
%  \centering
%  \begin{tabular}{lll}
%    \toprule
%    \multicolumn{2}{c}{Part}                   \\
%    \cmidrule{1-2}
%    Name     & Description     & Size ($\mu$m) \\
%    \midrule
%    Dendrite & Input terminal  & $\sim$100     \\
%    Axon     & Output terminal & $\sim$10      \\
%    Soma     & Cell body       & up to $10^6$  \\
%    \bottomrule
%  \end{tabular}
%\end{table}
%\usepackage[pdftex]{graphicx} ...
%\includegraphics[width=0.8\linewidth]{myfile.pdf}

>>>>

\section{Logistic Regression Experiment Details}\label{app:logistic}
In this section, we go over the details of our logistic regression experiment. The feature vector is the pix value of one image, which are normalized between 0 and 1.0. For simplification, we only have digits one (i.e. output $y = 1$) and seven (i.e. output $y = -1$). The probability of the $i^{th}$ output $y_i \in \{-1,+1\}$ with the input vector $x_i$ is $p(y_i \mid x_i) = \frac{1}{1+\exp (-y_i \theta^T x_i)}$, where $\theta$ are the parameters. We use the uniform prior distribution to represent that we do not have more information about $\theta$.

The proposer is random walk proposer, which can be modelled as: $\theta' = \theta_i + \mathcal{N}(0, \sigma^2I)$, where $\theta_i$ is the previous parameter vector, $\theta'$ is the proposed parameter vector, and we choose the variance $\sigma^2 = 0.01$. We initialize the $\theta$ to be all ones, so that we need sample more to access to the MAP.

For our minibatch MH testing, in order to control the ${\rm Sd} (\Delta') \leq 1.2$, we initialize the temperature $T_0 = 3000$, and decrease it by rule: $T_i =  T_0 /(i + 1)^{3} \mbox{ for } i \leq N/2 \mbox{ and } = T_0 /(i + 1)^{0.2} \mbox{ for } i >N/2 $, where $N=4000$ is total number of iteration. If the estimation of ${\rm Sd} (\Delta') > 1.2$, we ignore the current iterartion. The our estimation of ${\rm Sd} (\Delta')$ versus iteration number can be found in Fig.~\cite{fig:appendixExp2}. We choose our minibatch size equal to 50.

\begin{figure}[t]
  \centering
  \includegraphics[width=1\linewidth]{./figures/appendixExp2}
  \caption{Addition results for logistic regression experiment}
  \label{fig:appendixExp2}
\end{figure}

For adaptive MH testing, all the parameters are the same except they do not have the temperature term. The minibatch size of adaptive MH testing is initialized as 50, but it may increase. The Fig.~\cite{fig:appendixExp2}. shows the histogram of the actual minibatch size in adaptive MH testing.

@@

In this section, we show the details of our neural network experiment. We use four-layer fully connected neural network to solve this classification problem. The first layer is an input layer, the last layer is softmax layer, each intermediate layer is linear, sigmoid, and batch normailization. We use the SGHMC as the proposer for our minibatch MH testing. For the baseline, we use a tuned adaptive gradient descent optimizer, whose stepsize changes by $0.01 /(i+1)^{0.4}$. All of methods have minibatch size equal to 200. The total number of data instance is 1,000,000.

For SGHMC, we use the simplified update equation ~\cite{sghmc_2014}:
\[\Delta \theta = v \mbox{ , } \Delta v = -\eta \nabla U(\theta) - \alpha v + \mathcal{N}(0, 2(\alpha -\hat{\beta}) \eta), \]
where $v$ is auxiliary momentum variables, $\theta$ is our parameters, $\nabla U(\theta)$ is the gradient. We set the hyperparameter $\eta_i = 0.01 /(i+1)^{0.4}$, and $\alpha=0.1$. We use empirical Fisher information $V(\theta)$ to estimate value of $\hat{\beta}$, so that $\hat{\beta}=\frac{1}{2}\eta V(\theta)$ ~\cite{conf/icml/AhnBW12}.

In order to control the ${\rm Sd}(\Delta')$, we initialize temperature as 1000, and set temperature at iteration $i$ is $T_i = 1000/(i+1)^{0.5}$. But if temperature is smaller than one, we will just use one as its value.
% Daniel: here are example LaTeX codes for figures and tables if we want to use them.
%\begin{figure}[h]
%  \centering
%  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
%  \caption{Sample figure caption.}
%\end{figure}
%\begin{table}[t]
%  \caption{Sample table title}
%  \label{sample-table}
%  \centering
%  \begin{tabular}{lll}
%    \toprule
%    \multicolumn{2}{c}{Part}                   \\
%    \cmidrule{1-2}
%    Name     & Description     & Size ($\mu$m) \\
%    \midrule
%    Dendrite & Input terminal  & $\sim$100     \\
%    Axon     & Output terminal & $\sim$10      \\
%    Soma     & Cell body       & up to $10^6$  \\
%    \bottomrule
%  \end{tabular}
%\end{table}
%\usepackage[pdftex]{graphicx} ...
%\includegraphics[width=0.8\linewidth]{myfile.pdf}
